Staged Abstract Interpreters

### 2019-03-30 paper/50_stageabs.tex
misc

\paragraph{What the generated code look like?} In the generated code, all the
primitive operations (such as @eval@, @fix@, @ap_clo@, etc.) and monadic
operations (such as @flatMap@ and @map@) are eliminated. The residual program
consists of statements and expressions that purely manipulate the environment,
store, and two caches, whose underlying representations are all @Rep[Map[K,V]]@. We
also have several operations on tuples and lists, which are residualized from
the use of monads internally.

>>>>

\paragraph{What does the generated code look like?} In the generated code, all the
primitive operations (such as @eval@, @fix@, @ap_clo@, etc.) and monadic
operations (such as @flatMap@ and @map@) are eliminated. The residual program
consists of statements and expressions that purely manipulate the environment,
store, and two caches, whose underlying representations are all @Rep[Map[K,V]]@. We
also have several operations on tuples and lists, which are residualized from
the use of monads internally.

### 2019-03-30 paper/70_eval.tex
misc

We implement the abstract interpreters for control-flow analysis, i.e., a
value-flow analysis focus on lambda terms in functional languages. A frontend
desugars Scheme to a small core language that make the analyzer easy to
implement. Macros and @call/cc@ is not handled. As described in Section ???, we
implement a monovariant 0-CFA-like analysis, a context-sensitive $1$-CFA-like
analysis, both their versions with and without store-widening.

@@

\paragraph{Benchmarks} \todo{Rewrite}
The benchmark programs we used are collected from previous papers
\cite{Johnson:2013:OAA:2500365.2500604, ashley:practical,
DBLP:journals/corr/abs-1102-3676} and exisiting artifacts
\footnote{https://github.com/ilyasergey/reachability}.

We used the following benchmark programs:

@@

\begin{figure}[h]
\tiny
\begin{tabular}{@{}lllll@{}}
\toprule
    Program          &\#AST & unstaged   & staged     & $\Delta$ \\ \midrule
  % fib              &      & 1.020      & 2.046      & -50.14\%          \\
    @rsa@            &      &            &            & \%          \\
    @kcfa3@          &      &            &            & \%          \\
    @church@         &      &            &            & \%          \\
    @fermat@         &      &            &            & \%          \\
    @kcfa-worst-16@  &  198 & 0.352      & 0.028      & +1157.14\%        \\
    @kcfa-worst-32@  &  390 & 4.234      & 0.289      & +1365.05\%          \\
    @kcfa-worst-64@  &  774 & 61.475     & 4.425      & +1289.27\%         \\
    \bottomrule
\end{tabular}
\caption{Evaluation result for 0CFA without store-widening.} \label{evaluation_result}
\end{figure}

>>>>

We implement the abstract interpreters for control-flow analysis, i.e., a
value-flow analysis focus on lambda terms in functional languages. A frontend
desugars Scheme to a small core language that make the analyzer easy to
implement. Macros and @call/cc@ is not handled. As described in Section
\ref{cfa}, we implement a monovariant 0-CFA-like analysis, a context-sensitive
$1$-CFA-like analysis, both their versions with and without store-widening.

@@

\paragraph{Benchmarks} \todo{Rewrite}
The benchmark programs we used are collected from previous papers
\cite{Johnson:2013:OAA:2500365.2500604, ashley:practical,
DBLP:journals/corr/abs-1102-3676} and exisiting artifacts
\footnote{https://github.com/ilyasergey/reachability} for control-flow analysis.
We used the following benchmark programs:

@@

\begin{figure}[h]
\tiny
\begin{tabular}{@{}lllll@{}}
\toprule
    Program          &\#AST & unstaged   & staged     & $\Delta$ \\ \midrule
    @rsa@            &      &            &            & \%          \\
    @kcfa3@          &      &            &            & \%          \\
    @church@         &      &            &            & \%          \\
    @fermat@         &      &            &            & \%          \\
    @kcfa-worst-16@  &  198 & 0.352      & 0.028      & +1157.14\%        \\
    @kcfa-worst-32@  &  390 & 4.234      & 0.289      & +1365.05\%          \\
    @kcfa-worst-64@  &  774 & 61.475     & 4.425      & +1289.27\%         \\
    \bottomrule
\end{tabular}
\caption{Evaluation result for 0CFA without store-widening.} \label{evaluation_result}
\end{figure}
